Bacterial Microbiome and Obesity Meta-analysis Supplemental

### 2016-06-03 results/tables/table_1.Rmd
Add sequencing information

@@

@@

	list(study = capwords(study),
				n_subjects = n_subjects,
				per_obese = per_obese,
				bmi_summary = bmi,
				per_female = per_female,
				age_summary = age,
				per_white = per_white,
				beta_p = format_p(beta_summary[study,'p_value']))
}

@@

table1 <- kable(study_summary, row.names=FALSE, col.names=c("Study", "Subjects (N)", "Obese (%)", "Average BMI (Min-Max)", "Female (%)", "Average Age (Min-Max)", "Non-Hispanic White (%)", "AMOVA (P-value)"), align=c('l',rep('c', 7)), digits=3)

>>>>

---
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=0.75in
---

**Table 1. Summary of obesity, demographic, sequencing, and beta-diversity analysis data for the studies used in the meta-analysis.** NA indicates that those metadata were not available for that study.

```{r results='asis', echo=FALSE, warning=FALSE, eval=TRUE}
source('code/utilities.R')
get_dependencies('xtable')

options(xtable.sanitize.text.function=identity)

@@

region <- c(
	baxter = "V4",
	escobar = "V2",
	hmp = "V3-V5",
	ross = "V1-V3",
	schubert = "V4",
	turnbaugh = "V2",
	wu = "V1-V2",
	zupancic = "V3-V5",
	goodrich = "V4",
	zeevi = "V3-V4"
)

technology <-  c(
	baxter = "MiSeq",
	escobar = "454",
	hmp = "454",
	ross = "454",
	schubert = "MiSeq",
	turnbaugh = "454",
	wu = "454",
	zupancic = "454",
	goodrich = "MiSeq",
	zeevi = "MiSeq"
)

@@

	list(study = capwords(study),
				n_subjects = as.character(n_subjects),
				per_obese = per_obese,
				bmi_summary = bmi,
				per_female = per_female,
				age_summary = age,
				per_white = per_white,
				method = technology[study],
				region = region[study],
				beta_p = format_p(beta_summary[study,'p_value']))
}

@@

#colnames(study_summary) <- LETTERS[1:8]
colnames(study_summary) <- c("Study", "\\bigcell{c}{Subjects \\\\ (N)}",
													"\\bigcell{c}{Obese \\\\ (\\%)}",
													"\\bigcell{c}{Average BMI \\\\ (Min-Max)}",
													"\\bigcell{c}{Female \\\\ (\\%)}",
													"\\bigcell{c}{Average Age \\\\ (Min-Max)}",
													"\\bigcell{c}{Non-Hispanic \\\\ White (\\%)}",
													"\\bigcell{c}{Sequencing \\\\ Method}",
													"\\bigcell{c}{16S rRNA \\\\ Gene Region}",
													"\\bigcell{c}{AMOVA \\\\ (P-value)}")

colnames(study_summary) <- paste0("\\textbf{", colnames(study_summary), "}")

composite <- xtable(study_summary, label="")

align(composite) <- "llccccccccc"

print(composite,
		include.rownames=FALSE,
		include.colnames=TRUE,
		hline.after = c(-1,0, nrow(composite)),
		comment=FALSE,
		size="scriptsize",
		table.placement="!ht"
		)
```
